%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%! xelatex draft.tex
%! makeindex draft.nlo -s nomencl.ist -o draft.nls

\documentclass{hi-thesis}
\renewcommand{\quote}[2]{\noindent \emph{#2}\hfill{\bf #1}\\\\}
\usepackage{soul}

\begin{document}
% Basic front matter
\pagestyle{plain} \pagenumbering{roman}

\HeaderQuote{If you don't know where you are going, any road will take you there. }{Lewis Carroll} 

\chapter*{Alice's Adventures in Wonderland}
%Quotes from \emph{Alice's Adventures in Wonderland} \citeyearpar{alice} by Lewis \citeauthor{alice}.

\quote{Alice}{What is the use of a book, without pictures or conversations?} 
\quote{Rabbit}{Oh my ears and whiskers, how late it's getting!}
\quote{Alice}{Curiouser and curiouser!}
\quote{Alice}{\st{I wonder if I've been changed in the night? Let me think. Was 
I the same when I got up this morning? I almost think I can remember feeling a 
little different. But if I'm not the same, the next question is `Who in the 
world am I?' Ah, that's the great puzzle!}\\PAPER III -- InRu12}
\quote{Eaglet}{Speak English! I don't know the meaning of half those long 
words, and I don't believe you do either!}
\quote{Alice}{\st{I can't explain myself, I'm afraid, Sir, because I'm not myself you see.}\\PROBLEM STRUCTURE (APPENDIX)}
\quote{The Duchess}{\st{If everybody minded their own business, the world would 
go around a great deal faster than it does.} \\ PAPER VI -- InRu15b}
\quote{Alice}{\st{If it had grown up, it would have made a dreadfully ugly child; but it makes rather a handsome pig, I think.}\\PROBLEM INSTANCES}
\quote{The Cat}{We're all mad here.}
\quote{The Hatter}{ \st{Why is a raven like a writing desk?}\\SURROGATE MODELS}
\quote{The Hatter}{Twinkle, twinkle, little bat! How I wonder what you're at.}
\quote{The Queen}{Off with her head!}
\quote{The Duchess}{\st{Tut, tut, child! Everything's got a moral, if only you can find it.}\\CONCLUSIONS}
\quote{The Duchess}{\st{Take care of the sense, and the sounds will take care 
of themselves.}\\PAPER II -- InRu11b}
\quote{The Mock Turtle}{We called him Tortoise because he taught us.}
\quote{The Mock Turtle}{\st{Reeling and Writhing, of course, to begin with, 
and then the different branches of arithmetic -- Ambition, Distraction, 
Uglification, and Derision.}\\PAPER IV -- InRu15a}
\quote{The Mock Turtle}{Well, I never heard it before, but it sounds uncommon nonsense.}
\quote{The King}{\st{Begin at the beginning and go on till you come to the end: then stop.} \\INTRODUCTION}
\quote{Alice}{\st{I don't believe there's an atom of meaning in it.}\\ 
ANALYSING OPTIMAL SOLUTIONS}
\quote{The Queen}{\st{Sentence first -- verdict afterwards.}\\PROBLEM STRUCTURE}
\quote{Alice}{You're nothing but a pack of cards!}
\quote{Alice}{\st{But then, shall I never get any older than I am now? That'll 
be a comfort, one way -- never to be an old woman -- but then -- always to have 
lessons to learn!}\\PAPER VII -- InRu15c}
\quote{Alice}{\st{A cat may look at a king. I've read that in some book, but I don't remember where.}\\REFERENCES}
\quote{Alice}{I think I should understand that better, if I had it written down: but I can't quite follow it as you say it.}
\quote{The Duchess}{That's nothing to what I could say if I chose. }
\quote{The Queen}{Now, I give you fair warning, either you or your head must be off, and that in about half no time! Take your choice!}
\quote{Alice}{\st{It would be so nice if something made sense for a 
change.}\\PAPER IV -- InRu14}
\quote{Doorknob}{\st{Read the directions and directly you will be directed in the right direction.}\\SCHEDULING}
\quote{Mad Hatter}{No wonder you're late. Why, this watch is exactly two days slow.}
\quote{Alice}{Let me see: four times five is twelve, and four times six is thirteen, and four times seven is -- oh dear! I shall never get to twenty at that rate!}
\quote{Alice}{\st{It was much pleasanter at home, when one wasn't always growing larger and smaller, and being ordered about by mice and rabbits.}\\GENERATING TRAINING DATA}
\quote{Alice}{Well! I've often seen a cat without a grin; but a grin without a cat! It's the most curious thing I ever say in my life!}
\quote{The Duchess}{\st{There's a large mustard-mine near here. And the moral of that is -- The more there is of mine, the less there is of yours.}\\EVOLUTIONARY SEARCH}
\quote{The Mock Turtle}{\st{What is the use of repeating all that stuff, if you don't explain it as you go on? It's by far the most confusing thing I ever heard!}\\ORDINAL REGRESSION}
\quote{The Mock Turtle}{Ah! Then yours wasn't a really good school. Now at ours they had at the end of the bill. French, music, and washing -- extra.}
\quote{Alice}{Oh, how I wish I could shut up like a telescope! I think I could, if I only knew how to begin.}
\quote{Alice}{\st{But it's no use going back to yesterday, because I was a different person then.}\\CONFERENCE PROCEEDINGS}
\quote{Alice}{It was much pleasanter at home, when one wasn't always growing larger and smaller, and being ordered about by mice and rabbits.}
\quote{The Gryphon}{\st{The adventures first... explanations take such a dreadful time.}\\LEARNING MODELS}
\quote{Narrator}{Either the well was very deep, or she fell very slowly, for she had plenty of time as she went down to look about her and to wonder what was going to happen next.}
\quote{Alice}{Let me see: four times five is twelve, and four times six is thirteen, and four times seven is - oh dear! I shall never get to twenty at that rate! However, the Multiplication Table doesn't signify: let's try Geography. London is the capital of Paris, and Paris is the capital of Rome, and Rome - no, that's all wrong, I'm certain! I must have been changed for Mabel!}


\HeaderQuote{I have proved by actual trial that a letter, that takes an hour to write, takes only about 3 minutes to read}{Lewis Carroll} 

\chapter*{Through the Looking-Glass}
%Quotes \emph{Through the Looking-Glass, and What Alice Found There} \citeyearpar{lookingglass} by Lewis \citeauthor{lookingglass}.
\quote{The Queen}{It's a poor sort of memory that only works backward.}
\quote{The Queen}{Now, here, you see, it takes all the running you can do, to keep in the same place. If you want to get somewhere else, you must run at least twice as fast as that! }
\quote{Alice}{Now, Kitty, let's consider who it was that dreamed it all. This is a serious question, my dear, and you should not go on licking your paw like that -- as if Dinah hadn't washed you this morning!}
\quote{Alice}{You see, Kitty, it must have been either me or the Red King. He was part of my dream, of course -- but then I was part of his dream, too! Was it the Red King, Kitty? You were his wife, my dear, so you ought to know -- oh, Kitty, do help to settle it! I'm sure your paw can wait!" But the provoking kitten only began on the other paw, and pretended it hadn't heard the question.}
\quote{The Queen}{Sometimes I've believed as many as six impossible things before breakfast. }
\quote{The Queen}{Always speak the truth, think before you speak, and write it down afterwards.}

\HeaderQuote{She generally gave herself very good advice, (though she very 
seldom followed it).}{Lewis Carroll}
\nocite{lookingglass,alice}
\bibliographystyle{abbrvnat} 
\bibliography{papers/references}

\end{document}
