\HeaderQuote{But it's no use going back to yesterday, because I was a different 
person then.}{Alice}
\chapter{\usebibentry{InRu11a}{title}}\label[paper]{InRu11a}
\paper{natbib=InRu11a,file={papers/InRu11a.pdf},
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson}}

\HeaderQuote{Take care of the sense, and the sounds will take care of 
themselves.}{The Duchess}
\chapter{\usebibentry{InRu11b}{title}}\label[paper]{InRu11b}
\paper{natbib=InRu11b,file={papers/InRu11b.pdf},
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson}}

\HeaderQuote{I wonder if I've been changed in the night? Let me think. Was I 
the same when I got up this morning? I almost think I can remember feeling a 
little different. But if I'm not the same, the next question is `Who in the 
world am I?' Ah, that's the great puzzle!}{Alice}
\chapter{\usebibentry{InRu12}{title}}\label[paper]{InRu12}
\paper{natbib=InRu12,file={papers/InRu12.pdf},
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson}}

\HeaderQuote{It would be so nice if something made sense for a change.}{Alice}
\chapter{\usebibentry{InRu14}{title}}\label[paper]{InRu14}
\paper{natbib=InRu14,file={papers/InRu14.pdf},
    remark=\todoPapers{Find second publication for \cref{InRu14} -- Selected 
    papers ISI?}
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson}}

\HeaderQuote{Now, I give you fair warning, either you or your head must be off, 
and that in about half no time! Take your choice!}{The Queen}
\chapter{\usebibentry{InRu15a}{title}}\label[paper]{InRu15a}
\paper{natbib=InRu15a,file={papers/InRu15a.pdf},
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson},
    remark=Nominated for best paper award}

\HeaderQuote{But then, shall I never get any older than I am now? That'll be a 
  comfort, one way -- never to be an old woman -- but then -- always to have 
  lessons to learn!}{Alice}
\chapter{\usebibentry{InRu15b}{title}}\label[paper]{InRu15b}
\paper{natbib=InRu15b,file={papers/InRu15b.pdf},  
    authorslist={Helga Ingimundardóttir, Tómas Philip Rúnarsson},
    remark=Accepted\todoPapers{\Cref{InRu15b} not yet submitted}}